```{r, include=FALSE}
library(jsonlite)
jobs <- fromJSON("./data/topics/jobs.json")
```

## Jobs

The job filter of the topic search tool on the Open Discourse website is based on job groups. The job descriptions are taken from the [Politicians Table]. Since the `profession` does not follow a strict categorical system and hence has many unique values, we applied a grouping logic. We created seven groups in total. Politicians can only be assigned to one single group.

The tables below depict the character strings that need to be present in the job description of a politician to get assigned to the respective group.

When the assignment of a politician to a job group is ambiguous (e.g. multiple job descriptions) the politician is not assigned to any group.

### Recht

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
jobs[1] %>% 
  as_tibble() %>% 
  make_table(scrollable = TRUE)
```

### Wirtschaft

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
jobs[2] %>% 
  as_tibble() %>% 
  make_table(scrollable = TRUE)
```

### Naturwissenschaft

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
jobs[3] %>% 
  as_tibble() %>% 
  make_table(scrollable = TRUE)
```

### Gesellschaftswissenschaft

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
jobs[4] %>% 
  as_tibble() %>% 
  make_table(scrollable = TRUE)
```

### Agrar

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
jobs[5] %>% 
  as_tibble() %>% 
  make_table(scrollable = TRUE)
```

### Journalismus

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
jobs[6] %>% 
  as_tibble() %>% 
  make_table(scrollable = TRUE)
```

### Handwerk

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
jobs[7] %>% 
  as_tibble() %>% 
  make_table(scrollable = TRUE)
```
