---
title: "Open Discourse - Documentation"
author: "Open Discourse Team"
date: "`r Sys.Date()`"
site: bookdown::gitbook
documentclass: book
link-citations: yes
description: "This is the official documentation of the Open Discourse project"
url: https\://opendiscourse.de
github-repo: open-discourse/open-discourse
---

```{r, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r, table print helper, include=FALSE, echo=FALSE}

make_table <- function(x, scrollable = FALSE){
  if(scrollable == TRUE){
    x %>%
      kableExtra::kable(format = "html", booktabs = TRUE) %>%
      kableExtra::kable_styling(font_size = 12, position = "center") %>%
      kableExtra::scroll_box(width = "100%", height = "300px")
  } else{
    x %>% kableExtra::kable(format = "html", booktabs = TRUE) %>%
      kableExtra::kable_styling("striped", latex_options = "striped", position = "center") %>%
      kableExtra::column_spec(1, bold = TRUE)
  }

}
```

# Introduction

This is the official documentation space of the [Open Discourse](opendiscourse.de) project.

Currently you can find detailed documentation about these topics:


-   [Get the Data]
-   [Data Report of the Database]
-   [LDA Topic Model]



------------------------------------------------------------------------
:::: {.infobox .caution}
**Citing Open Discourse**

If you want to cite the Open Discourse corpus, please cite the resource by referring to the associated data paper published at the Harvard Dataverse as:

> *Richter, F.; Koch, P.; Franke, O.; Kraus, J.; Kuruc, F.; Thiem, A.; Högerl, J.; Heine, S.; Schöps, K., 2020, "Open Discourse", <https://doi.org/10.7910/DVN/FIKIBO>, Harvard Dataverse*
::::

