---
title: "Documentation Space - Open Discourse v. `r paste(current_version_tag)`"
author: "Open Discourse Team"
date: "`r Sys.Date()`"
site: bookdown::gitbook
documentclass: book
link-citations: yes
description: This is the official documentation of the Open Discourse project
url: https\://opendiscourse.de
github-repo: open-discourse/open-discourse
---

```{r, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r, table print helper, include=FALSE, echo=FALSE}

make_table <- function(x, scrollable = FALSE){
  if(scrollable == TRUE){
    x %>%
      kableExtra::kable(format = "html", booktabs = TRUE) %>%
      kableExtra::kable_styling(font_size = 12, position = "center") %>%
      kableExtra::scroll_box(width = "100%", height = "300px")
  } else{
    x %>% kableExtra::kable(format = "html", booktabs = TRUE) %>%
      kableExtra::kable_styling("striped", latex_options = "striped", position = "center") %>%
      kableExtra::column_spec(1, bold = TRUE)
  }

}
```

# Introduction

This is the official documentation space of the [Open Discourse](opendiscourse.de) project.

Currently you can find detailed documentation about these topics:

-   [Get the Data]

-   [Data Report of the Database]

-   [LDA Topic Model]

------------------------------------------------------------------------

**Current State of Open Discourse:**

The latest session covered in the current database version took place at `r max(speeches$date)`. 
Please note that GitHub and Harvard Dataverse use different versioning schemes. Therefore the version numbers of the Open Discourse database differ between the two platforms. 

The latest GitHub version number of Open Discourse is  `r gh_version_history[1,1]` and was created on `r gh_version_history[1,2]`. This GitHub version corresponds with the latest Harvard Dataverse version number `r hdv_version_history[1,1]` created on `r hdv_version_history[1,2]`

::: {.infobox .caution}
**Citing Open Discourse**

If you want to cite the Open Discourse corpus, please cite the resource as follows:

> `r sprintf("Richter, F.; Koch, P.; Franke, O.; Kraus, J.; Kuruc, F.; Thiem, A.; Högerl, J.; Heine, S.; Schöps, K. (2020). Open Discourse. <https://doi.org/10.7910/DVN/FIKIBO>. Harvard Dataverse. V%s.", hdv_version_history[1,'v'])`
:::
